A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-10 12_conclusions_future_work.tex
mention back pressure compensation as contribution in intro and conclusion

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{ and we introduced beading schemes which improve on the state-of-the-art.}

>>>>

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{
we introduced beading schemes which improve on the state-of-the-art
and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
}

### 2019-12-10 1_intro.tex
mention back pressure compensation as contribution in intro and conclusion

In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill. 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

@@

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which
\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be generally below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\end{itemize}

>>>>

In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state-of-the-art.} 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
\revise{
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
}{Furthermore we present an approach to accurately realize adaptive bead width.
}
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

@@

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which
\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be generally below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}
